An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-19 paper/paper.tex
Update paper with results of spdyathome

\documentclass[11pt,letterpaper,notitlepage]{article}

\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{clrscode3e}
\usepackage{appendix}
\usepackage{framed}
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{sec:background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
HTTP is one of the most widely used application-level protocols. Initially
written in 1996~\cite{http1rfc}, HTTP was written for a different era of web
sites -- before streaming video websites, before asset-heavy web pages, and
before mostly-Javascript web applications like Google's Gmail, Twitter, and
Facebook.

@@

The current self-imposed deadline for HTTP/2.0 is July
2013~\cite{httpbis-charter}.  So far, three likely starting points for
the specification have been proposed: Google's SPDY, Microsoft's Speed +
Mobility, and a ``Network-Friendly'' proposal from a handful of Open Source
authors. The three will be briefly outlined beginning in
\S\ref{sec:background/spdy} and then the remainder of the paper will focus on
measurements of the most viable candidate for HTTP/2.0, SPDY.

@@

From this data, we analyzed the theoretical benefit of asset combination for SPDY in Section \ref{sec:assets}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Client/Server Implementation}
\label{sec:research/client-server}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The simulation uses a client-server architecture to gather data about the
effectiveness of the SPDY protocol. The server can be run from any standard
machine, but only a single one will be run for the experiment.  The client (the
``collector'') is the real measurement platform and will be distributed to
volunteers to run in order to test SPDY in a number of different network
conditions.  The client will collect data and report back to the server
anonymous information about how performant the protocol was in addition to
helpful details that may help break down what caused variations in results.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Server}
\label{sec:research/server}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If each client accessed all of the websites we scraped, the process would take
an insufferably long time.  Therefore, we have decided on the following
breakdown
\begin{center}
\begin{tabular}{ccc}
$1-100$ top sites & 10\% of $100-1000$ sites & 1\% of $1000-10000$ sites \\
\end{tabular}
\end{center}

These sites will be selected randomly and made into a list for the client to
consume. This is a total of 280 sites that run the gamut from representing the
largest and most frequented sites on the web, down to some of the most obscure.

The client can access the server using standard RESTful paths in two fashions
\begin{itemize}
\item \texttt{/site/<n>} where \texttt{n} is an integer that specifies the index
of the website simulation that is being accessed.  This will result in the
server returning fully formed HTML containing assets that map to the proper size
of the assets from the scraped page.  The rest of the document will be filled
with random bytes until it is the proper size of the recorded webpage that was
scraped.
\item \texttt{/img/<m>} where \texttt{m} is an integer specifying the size of the
asset that should be downloaded. So, in the case that we found a 2 MB image on a
webpage that is being simulated, \texttt{m} will be 2,000,000 and the server
will return a binary blob of that size. It is possible that this could take into
account the different compressibility of text to images.  For instance, an asset
that was javascript should have somewhat less random data supplied so that it
may compress more readily as compared to an image which doesn't compress very
much on top of its generally pre-compressed format.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Client}
\label{sec:research/client}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The client should be cross platform and easy to run.  The ultimate goal is for
it to be as simple as downloading and clicking on an executable of some form.
The client will access each of the tests specified in the list in turn using
both SPDY and HTTP/1.1 with SSL/TLS and
record timing information about how long it takes for each request to complete.
After this step is complete, the client will gather data about its location and
other considerations in order to return to the server for analysis.  All data
returned will be presented to the user to approve \textbf{before} being sent
back.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real World SPDY vs. HTTP}
\label{sec:realworld}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
here is where we will discuss brian's spdyathome results

% I don't want to remove this wholesale but I don't think it is relevant
% anywhere else in the paper. Maybe it fits somewhere?
% -Tom
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Evaluation}
% \label{sec:eval}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Once this data is collected the time difference will be found between each
% protocol's retrieval of each test page. The obvious next step will be to
% determine if SPDY actually made the pages load faster or not. In all likelihood,
% there will not be a constant speedup across all pages and so the next step of
% evaluation will be to see in which cases an improvement was found. This should
% give insight into how SPDY improves over the prior specification and help decide
% whether or not it is worth it for the actual upgrade of HTTP to take place.
%
% This success of this experiment will be based off of how many points of data can
% be acquired and how varying the conditions are for them.  Much of what will be
% included in the final report will be plots and tables of the data collected to
% allow the reader to decide for themselves.  This information will be useful to
% others and the measurement platform itself should be designed in such a way that
% future experiments can be run on it without too much effort to retool it.

@@

>>>>

\documentclass[10pt,letterpaper,notitlepage]{article}

\usepackage{fullpage}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{clrscode3e}
\usepackage{appendix}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{float}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{sec:background}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
HTTP is one of the most widely used application-level protocols. Initially
written in 1996~\cite{http1rfc}, it was created for a different era of web
sites -- before streaming video websites, before asset-heavy web pages, and
before mostly-Javascript web applications like Google's Gmail, Twitter, and
Facebook.

@@

The current self-imposed deadline for HTTP/2.0 is July
2013~\cite{httpbis-charter}.  So far, three likely starting points for
the specification have been proposed: Google's SPDY, Microsoft's Speed +
Mobility, and a ``Network-Friendly'' proposal from a handful of Open Source
authors. The three will be briefly outlined beginning in
\S\ref{sec:background/spdy} and then the remainder of the paper will focus on
measurements of the most viable candidate for HTTP/2.0 -- SPDY.

@@

From this data, we analyzed the theoretical benefit of asset combination for
SPDY in \S\ref{sec:assets}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Client/Server Implementation}
\label{sec:research/client-server}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The simulation uses a client-server architecture to gather data about the
effectiveness of the SPDY protocol. The server can be run from any standard
machine, but only two will be run for the experiment.  The client (the
``collector'') is the real measurement platform and has been distributed to
volunteers to run in order to test SPDY in a number of different network
conditions.  The client collects data and reports back to the server
anonymous information about how performant the protocol was in addition to
helpful details that may help break down what caused variations in results.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Server}
\label{sec:research/server}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
If each client accessed all of the websites we scraped, the process would take
an insufferably long time.  Therefore, we have decided on the following
breakdown
\begin{center}
\begin{tabular}{ccc}
$1-100$ top sites & 10\% of $100-1000$ sites & 1\% of $1000-10000$ sites \\
\end{tabular}
\end{center}

These sites have been selected randomly and made into a list for the client to
consume. This is a total of 280 sites that run the gamut from representing the
largest and most frequented sites on the web, down to some of the most obscure.
The full list of sites used is attached in Appendix~\ref{app:sitelist}.

The client can access the server using standard RESTful paths in two fashions
\begin{itemize}
\item \texttt{/site/<n>} where \texttt{n} is an integer that specifies the index
of the site to download. A simple JSON list of each of the assets for a site is
returned, in addition to random junk to fill the rest of the size of the page.

\item \texttt{/asset/<m>.(c|u)} where \texttt{m} is an integer specifying the size of the
asset that should be downloaded. So, in the case that we found a 2 MB image on a
webpage that is being simulated, \texttt{m} will be 2,000,000 and the server
will return a binary blob of that size. The \texttt{c} and \texttt{u} appended
to the end changes whether the asset should be compressed or not.  For instance, an asset
that was javascript should have somewhat less random data supplied so that it
may compress more readily as compared to an image which doesn't compress very
much on top of its generally pre-compressed format.
\end{itemize}

Each asset has been determined to either be ``primary'' or ``secondary'' with
primary assets coming from the original host server itself and secondary coming
from any other host.  An example of secondary assets would be Google ads.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Thor}
\label{sec:research/thor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Both the client and server use the Thor library for HTTP and SPDY communication.
They share a common core of TCP server and other utilities, so the comparison
between the two protocols is as close as possible.  The library had to be
updated to complete its support for SPDY, the version of the library that was
used for the project can be found at \url{https://github.com/bis12/thor}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Client}
\label{sec:research/client}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The client works in the following way
\begin{enumerate}
    \item Connect to the server and download the list of sites to access.
        Randomize the order of the sites and continue.
    \item Connect to each of these sites in turn with both HTTP and SPDY clients
        and download the asset list for each.  The order that HTTP and SPDY
        connect is randomized each time also.
    \item Download each of the assets for each site from either the primary or
        secondary host depending on the original location.
    \item Once all assets are fetched, or a certain timeout is reached, the TCP
        connections are torn down and the download of that site is considered
        complete or ends in an error.
\end{enumerate}
Once all of the sites have been downloaded, the results are collected and sent
back to the server, in addition to recording the IP address and a unique
identifier for the host so that repeats from the same location and computer can
be compared.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real World SPDY vs. HTTP}
\label{sec:realworld}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the following section we will present the results of the data collection and
a short analysis of the results.

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot1.eps}
\caption{A simple comparison of dowload times for each site downloaded across
all collections from all clients.  Positive is time saved by SPDY and negative
is time added.}
\label{fig:plot1}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot9.eps}
\caption{Similar to Figure~\ref{fig:plot1} except with each site averaged across
responses.}
\label{fig:plot9}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot3.eps}
\caption{This is identical to Figure~\ref{fig:plot1} except with each response
averaged across all of their sites.}
\label{fig:plot3}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot2.eps}
\caption{A scatter plot comparing time to download site to the average of the
    two times it took to download the site.  No correlation appears to be
present.}
\label{fig:plot2}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot8.eps}
\caption{Scatter of speedup vs the aggregate size in bytes of the site
downloaded.}
\label{fig:plot8}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot12.eps}
\caption{Scatter of speedup vs the aggregate size in bytes of a site averaged
across responders.}
\label{fig:plot12}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot10.eps}
\caption{Scatter of speedup vs the number of assets per site
downloaded.}
\label{fig:plot10}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot5.eps}
\caption{A plot to find if each unique responder with greater than 5 responses
had a similar result each time.}
\label{fig:plot5}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{plots/plot6.eps}
\caption{Similar to Figure~\ref{fig:plot1}, but simply in order of response
    rather than ordered by savings.  This is to find if some sort of confounding
variable affected the responses across some part of time.}
\label{fig:plot6}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Final Collections}
\label{sec:realworld/fc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
At the time of this analysis there were 41 unique responders from 42 unique IP
addresses. They combined for a total of 482 responses.  Each test took roughly
25 minutes to run, so it would be difficult to expand the test further in terms
of the number of sites downloaded.  The relatively small number of results makes
it difficult to accurately say anything about each responder in aggregate, but
this accounts for many tens of thousands of sites downloaded, so trends are
certainly evident and accurate with regards to the sites.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Analysis}
\label{sec:realworld/analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Each of the previous plots indicate one of two things
\begin{itemize}
    \item  There was no correlation between size of site, number of assets, or
        any other metric and the speedup from SPDY.
    \item There was practically no speedup from SPDY
\end{itemize}

This is contradictory to the results obtained by many other experimenters and
brings the accuracy of this experiment into question.  Clearly more work needs
to be done in order to find the cause of this discrepancy.  It seems likely that
the architecture of the server and client caused greater overheads with
variability than SPDY could have overcome and this hides the improvements made
with SPDY. It is also possible that there is an error in the implementation or
that some aspect of the design of the experiment is fundamentally flawed.  This
will need to be investigated before possibly going forward with this work.
% I don't want to remove this wholesale but I don't think it is relevant
% anywhere else in the paper. Maybe it fits somewhere?
% -Tom
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Evaluation}
% \label{sec:eval}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Once this data is collected the time difference will be found between each
% protocol's retrieval of each test page. The obvious next step will be to
% determine if SPDY actually made the pages load faster or not. In all likelihood,
% there will not be a constant speedup across all pages and so the next step of
% evaluation will be to see in which cases an improvement was found. This should
% give insight into how SPDY improves over the prior specification and help decide
% whether or not it is worth it for the actual upgrade of HTTP to take place.
%
% This success of this experiment will be based off of how many points of data can
% be acquired and how varying the conditions are for them.  Much of what will be
% included in the final report will be plots and tables of the data collected to
% allow the reader to decide for themselves.  This information will be useful to
% others and the measurement platform itself should be designed in such a way that
% future experiments can be run on it without too much effort to retool it.

@@

\appendix
\section{List of Sites Used in Experiment}
\label{app:sitelist}
\tiny
\begin{multicols}{4}
\begin{verbatim}
https://www.multiply.com
https://www.google.ru
http://www.rr.com
http://www.itimes.com
http://www.chinanews.com
http://www.livestream.com
https://www.google.com.hk
http://www.facemoods.com
http://www.ebay.de
http://www.2345.com
https://www.google.lk
https://www.thepiratebay.se
http://www.hao123.com
http://www.tmall.com
https://www.pinterest.com
https://www.google.com.br
http://www.slutload.com
https://www.maxbounty.com
https://www.thenextweb.com
https://www.google.es
http://www.wikihow.com
http://www.xscores.com
http://www.2ch.net
http://www.jrj.com.cn
https://www.facebook.com
https://www.apple.com
https://www.google.com.mx
http://www.actuweb.net
https://www.google.co.jp
https://www.godaddy.com
https://www.sueddeutsche.de
http://www.anonym.to
https://www.fotolia.com
http://www.imgur.com
https://www.sourceforge.net
http://www.espn.go.com
https://www.google.com
https://www.utoronto.ca
https://www.google.co.in
https://www.mailchimp.com
http://www.people.com
https://www.midphase.com
http://www.okbuy.com
http://www.yoka.com
http://www.4399.com
https://www.amazon.fr
http://www.livedoor.com
http://www.xhamster.com
http://www.tocmai.ro
http://www.vod.pl
https://www.citibank.com
http://www.anonymouse.org
https://www.youtube.com
http://www.vporn.com
http://www.zedo.com
http://www.lashou.com
https://www.google.co.nz
http://www.optymalizacja.com
https://www.yahoo.com
http://www.ldlc.com
http://www.detik.com
http://www.bunshun.jp
https://www.freedigitalphotos.net
http://www.imdb.com
https://www.odnoklassniki.ru
https://www.tu-chemnitz.de
http://www.statigr.am
http://www.avg.com
https://www.wordpress.com
http://www.directlyrics.com
http://www.bing.com
https://www.pornhub.com
https://www.aol.com
https://www.google.co.kr
https://www.americangreetings.com
https://www.adobe.com
http://www.trklnks.com
https://www.leagueoflegends.com
https://www.google.fr
http://www.funnyjunk.com
https://www.google.it
https://www.orkut.com
http://www.fc2.com
https://www.egopay.com
http://www.techcrunch.com
http://www.ask.com
https://www.zoopla.co.uk
https://www.join.me
https://www.google.ca
https://www.taz.de
http://www.soso.com
https://www.linkedin.com
https://www.mail2web.com
http://www.meristation.com
http://www.godlikeproductions.com
http://www.neogaf.com
https://www.google.co.il
https://www.amazon.de
http://www.taleo.net
http://www.babylon.com
http://www.taobao.com
http://www.reddit.com
https://www.amazon.co.jp
http://www.baidu.com
http://www.xvideos.com
http://www.lavanguardia.com
http://www.ntvmsnbc.com
http://www.nyaa.eu
http://www.wcarev.com
http://www.renren.com
http://www.rakuten.co.jp
http://www.neatorama.com
http://www.alibaba.com
https://www.live.com
https://www.sape.ru
https://www.googleusercontent.com
http://www.twitpic.com
https://www.sahibinden.com
https://www.google.com.pe
https://www.boards.ie
https://www.nix.ru
http://www.jimdo.com
http://www.lemonde.fr
http://www.zappos.com
https://www.smashwords.com
http://www.engadget.com
https://www.tumblr.com
https://www.google.dk
http://www.oriflame.com
http://www.ne.jp
https://www.vk.com
https://www.adnxs.com
http://www.majikichi.com
http://www.youporn.com
https://www.tagged.com
http://www.videoweed.es
https://www.spirithalloween.com
http://www.bbc.com
https://www.9gag.com
http://www.gizmodo.com
http://www.msn.com
http://www.linkwithin.com
http://www.vend-o.com
http://www.crsky.com
https://www.twitter.com
http://www.zedge.net
https://www.wordpress.org
http://www.amawebs.com
http://www.huffingtonpost.com
http://www.rediff.com
http://www.wigetmedia.com
https://www.dailymotion.com
http://www.yayabay.net
http://www.sogou.com
https://www.google.com.tr
https://www.livejournal.com
https://www.zopim.com
http://www.shaadi.com
http://www.medscape.com
https://www.flickr.com
http://www.ahram.org.eg
http://www.firstclass-download.com
https://www.conduit.com
https://www.careerbuilder.com
https://www.amazon.co.uk
https://www.backcountry.com
http://www.zippyshare.com
https://www.netflix.com
http://www.daum.net
http://www.yahoo.co.jp
http://www.slate.com
http://www.stackoverflow.com
http://www.matichon.co.th
http://www.politiken.dk
https://www.expedia.com
https://www.sportsmansguide.com
http://www.lastfm.es
https://www.amazon.com
http://www.tabnak.ir
https://www.adf.ly
https://www.blogspot.com
http://www.welt.de
https://www.instantcheckmate.com
http://www.hubpages.com
http://www.serialu.net
https://www.google.de
http://www.clubpenguin.com
https://www.vodafone.co.uk
http://www.pcmag.com
http://www.codecademy.com
http://www.t.co
http://www.mlb.com
https://www.redtube.com
http://www.ebay.com
http://www.go.com
http://www.instagram.com
http://www.28tlbb.com
https://www.google.com.au
http://www.about.com
https://www.blogger.com
http://www.extratorrent.com
http://www.digitaldesire.com
http://www.youtu.be
http://www.adultfriendfinder.com
https://www.ucm.es
http://www.vcommission.com
https://www.mail.ru
http://www.programme-tv.net
https://www.bbc.co.uk
http://www.hafeezcentre.pk
https://www.google.pl
https://www.google.co.id
http://www.ebay.co.uk
http://www.apontador.com.br
https://www.google.co.uk
https://www.wikipedia.org
https://www.web.com
http://www.ask.fm
http://www.craigslist.org
https://www.nokia.com
http://www.elahmad.com
https://www.jobrapido.com
http://www.yesky.com
http://www.tudou.com
https://www.hbr.org
http://www.khl.ru
http://www.flipora.com
http://www.babytree.com
http://www.pcauto.com.cn
http://www.1uuc.com
http://www.ifeng.com
http://www.youku.com
https://www.uchicago.edu
http://www.pptv.com
http://www.formulatv.com
http://www.searchengines.ru
http://www.cnn.com
http://www.fux.com
http://www.alisoft.com
http://www.drtuber.com
http://www.narod.ru
http://www.msn.com.cn
http://www.sohu.com
http://www.globalgrind.com
http://www.icicibank.com
http://www.ndtv.com
http://www.tuan800.com
http://www.yandex.ru
http://www.grindtv.com
http://www.w3schools.com
https://www.paypal.com
http://www.ccb.com
http://www.uol.com.br
http://www.mywebsearch.com
http://www.porntube.com
http://www.tinypic.com
http://www.hypergames.net
89909 http://www.tianya.cn
http://www.126.com
http://www.newbigtube.com
https://www.microsoft.com
http://www.chinaren.com
http://www.laptopmag.com
http://www.biglion.ru
http://www.weibo.com
http://www.xunlei.com
http://www.livejasmin.com
http://www.super.cz
https://www.fandango.com
\end{verbatim}
\end{multicols}
